%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Wilson Resume/CV
% XeLaTeX Template
% Version 1.0 (22/1/2015)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Howard Wilson (https://github.com/watsonbox/cv_template_2004) with
% extensive modifications by Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt]{article} % Default font size

\input{structure.tex} % Include the file specifying document layout

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\title{Mike Vanbuskirk -- Resume} % Print the main header

%------------------------------------------------

\parbox{0.5\textwidth}{ % First block
\begin{tabbing} % Enables tabbing
\hspace{3cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf Located} \> Seattle, WA\\ % Address line 1
\end{tabbing}}
\hfill % Horizontal space between the two blocks
\parbox{0.5\textwidth}{ % Second block
\begin{tabbing} % Enables tabbing
\hspace{3cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf Email} \> \href{mailto:mvanbus43@gmail.com}{mvanbus43@gmail.com} \\ % Email address
\end{tabbing}}

%----------------------------------------------------------------------------------------
%	IT/COMPUTING SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Core Technical Skills}

\skillgroup{\large Operating Systems}
{
\textbf{Linux/Unix} - CentOS, RHEL, Solaris, Debian/Ubuntu, XenVM, Amazon Linux\\
\textbf{Windows} - Server 2008/2012
}

%------------------------------------------------

\skillgroup{\large Programming/Scripting}
{
\textbf{BASH/Shell} - Automation \& system administration\\
\textbf{JSON} - Configuration file management\\
\textbf{Javascript} - Client-side scripting/interface\\
\textbf{Python} - Hardware device configuration \& system administration\\
\textbf{HTML/CSS} - Content mark-up\\
\textbf{LaTeX} - Document creation \& typesetting
}

%------------------------------------------------

\skillgroup{\large Applied}
{
\textbf{Networking} - Global-level DNS configuration \& traffic management, load-balancer configuration \& support, routing modification, VPN configuration \& support  \\
\textbf{Application Support} - Support \& management of highly available applications in cloud, CDN \& e-commerce infrastructures\\
\textbf{Development Technology} - DVCS(Git), continuous delivery, auto-scaling, environment deployment\\
\textbf{Project Management} - Agile/SCRUM\\
\textbf{Debugging/Troubleshooting} - Log analysis, application debugging, file dump analysis, HTTP header/response debugging, hardware failure analysis \\
\textbf{Service} - Tier-1 event management \& response, configuration change support, ticket \& queue handling, documentation management, PKI \& general authentication support
}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\tabbedblock{
\bf{2009-2012} \> BSc Networks Design \& Management - \href{http://www.wgu.edu}{Western Governors University} \\[3pt]
}

%----------------------------------------------------------------------------------------
%	EMPLOYMENT HISTORY SECTION
%----------------------------------------------------------------------------------------

\section{Employment History}

\job
{Jan 2016 -}{Present}
{Amazon, Seattle, WA - United States}
{http://aws.amazon.com}
{Technical Operations Team Lead}
{
\begin{itemize-noindent}
\item{Team Lead for Seattle-based Technical Operations Support Team.}
\item{Integrated as part of management team.}
\item{Ensure team of 15 engineers is delivering on SLAs and operational goals.}
\item{AGILE based project management and roadmap planning.}
\item{Point of escalation for ongoing service/event issues.}
\item{Ongoing engagement and project management with other service teams within Amazon.}
\end{itemize-noindent}

}
	
\job
{Sep 2014 -}{Present}
{Amazon, Seattle, WA - United States}
{http://aws.amazon.com}
{Technical Operations Support Engineer / Support Engineer III}
{
\begin{itemize-noindent}
\item{Tier-1 event management, application \& service support, configuration, monitoring, and automation across one of the largest e-commerce \& cloud platforms in the world.}
\item{Deployed code in continuous delivery to production monitoring system utilized globally by internal Amazon teams.}
\item{Helped define 1st-tier engagement policies for event response.}
\item{Supported \& configured multiple highly-available applications and services.}
\end{itemize-noindent}

}


%------------------------------------------------

\job
{Sep 2013 -}{Aug 2014}
{Level 3, Tulsa, OK - United States}
{http://www.level3.com}
{CDN/NOC Technician}
{
\begin{itemize-noindent}
\item{Monitor and maintain many thousand node global CDN platform, including highly available storage and streaming applications.}
\item{Tier-1 event management \& response(including 3rd party vendor engagement), real time alert analysis, triage, and application support.}
\item{Provided analysis and debugging output to Tier III engineering teams identifying a critical bug in global Java application.}
\item{Developed scripting to identify nodes approaching critical via historical alarm \& monitoring data analysis.}
\end{itemize-noindent}

}

%-------------------------------------------------

\exphilights{Additional Experience Hilights}
{
\textbf{Synergy Services} - Contract CDN Technician - Tulsa, OK\\
\textit{Jun 2013 - Sep 2013}\\ 
Rapid training and successful transition to full-time direct-hire monitoring technician with single responsibility inside the Level 3 CDN.\\

\textbf{Tech Specialties} - CEO/Consultant - Stillwater, OK\\
\textit{Feb 2010 - Sep 2014}\\ 
Provided IT consulting and support for small/medium business clients. Full ownership of project design, sale, implementation, and support.\\

\textbf{Petra} - Sales Acquisition Rep - Edmond, OK\\
\textit{Nov 2009 - Jan 2010}\\ 
Managed 1600 active and non-active accounts for national electronics wholesaler. Advised clients on marketing and profitable product strategies. Returned multiple accounts to purchasing status.\\

\textbf{OfficeMax} - Business Development Manager - Norman, OK\\
\textit{February 2009 - October 2009}\\ 
Managed 300 small/medium business accounts, including acquisition and development of new accounts. Exceeded both new business and current business goals in successive quarters.\\

\textbf{Dell Computers} - Inside Business Sales - Oklahoma City, OK\\
\textit{September 2006 - December 2008}\\ 
Inside business sales for one of the largest computer companies in the world. Consistently exceeded quota and progressed internally to relationship account roles.\\

\textbf{Ad Specialties of Stillwater} - Customer Relationship Manager - Stillwater, OK\\
\textit{August 2005 - August 2006}\\
Performed multiple duties including IT support, sales, accounts \& billing, copy-writing, graphic design, and marketing. Helped fulfil promotional product orders on multiple national campaigns.\\

\textbf{Convergys} - Customer Service Representative - Moore, OK\\
\textit{August 2005 - August 2006}\\
Provided support for billing and technical issues for national broadcast/content provider, including qualifying sales opportunities.\\

}

\end{document}
